---
main_topsize: 0.16 #percent coverage of the poster
main_bottomsize: 0.04
#ESSENTIALS
title: '**Open Educational Resources and Open Source Software**'
author:
  - name: '**Ralph-Uwe Börner**'
    affil: 1
    main: true
    #orcid: '0000-0002-1099-3857'
    #mastodon: ruboerner\@mastodon.social
    #github: github.com/ruboerner
    email: rub@gephysik.tu-freiberg.de
affiliation:
  - num: 1 
    address: Institute of Geophysics and Geoinformatics, TU Bergakademie Freiberg
main_findings:
  - "The potential of **Open Source Software** and **Open Educational Resources** for positive impacts on teaching, learning, and research is immense."
logoleft_name: TUBAF_Logo_EN_weiss.png
logocenter_name: TUBAF_Logo_EN_weiss.png
logoright_name: TUBAF_Logo_EN_weiss.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
#knit: pagedown::chrome_print
primary_colour: "#00477e"
secondary_colour: "#0064A8"
accent_colour: "#0064A8"
poster_width: 33.1in
poster_height: 46.8in
main_textsize: 90pt
title_textsize: 104pt
body_textsize: 50pt
author_textsize: 50pt
affiliation_textsize: 32pt
column_numbers: 1
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

This is the `posterdown_betterport` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

# Objectives

1.  Pick a template layout.
2.  Write/ create your poster content distraction free.
3.  Let posterdown do its thing!

```{r, out.width="120px", echo=FALSE}
library(qrcode)
code <- qr_code('http://tu-freiberg.de')
plot(code, col = c("white", "#00477e"))
```

# Methods

I will show here how to include poster elements that may be useful, such as equation using mathjax:
$$
E = mc^2 
$$
To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentence using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

***Now on to the results!***
